\cvsection{Experience}
\begin{cventries}
  \cventry
    {Research Assistant}
    {Virtual Reality and Immersive Visualization Group, RWTH Aachen}
    {Aachen, Germany}
    {January 2017 - Current}
    {
      \begin{cvitems}
        \item {Developed \textit{Polarized Light Imaging (PLI) Viewer}, a tool for visualizing 3D-PLI transmittance, retardation, direction and inclination maps. Also contains parallelized implementations of streamline tractography and fiber ODF computation.}
        \item {Developed \textit{cuSH}, an open source Cuda library for Spherical Harmonics (SH) which contains functionality for projecting spherical functions to finite SH expansions as well as common arithmetic in the SH basis. \\\href{https://devhub.vr.rwth-aachen.de/VR-Group/cuSH}{https://devhub.vr.rwth-aachen.de/VR-Group/cuSH}}
        %\item {Developed \textit{ecs}, a header-only C++ library which provides a generic implementation of the entity-component-system pattern. \\\href{https://devhub.vr.rwth-aachen.de/VR-Group/ecs}{https://devhub.vr.rwth-aachen.de/VR-Group/ecs}}
        \item {Supervised students in the Current Topics in the Field of Virtual Reality seminar.}
      \end{cvitems}
    }
  \cventry
    {Student Assistant}
    {Virtual Reality and Immersive Visualization Group, RWTH Aachen}
    {Aachen, Germany}
    {February 2016 - December 2016}
    {
      \begin{cvitems}
        \item {Contributed to the development of \textit{pvt}, an open-source library for visualizing computation performance data.\\\href{https://devhub.vr.rwth-aachen.de/VR-Group/pvt}{https://devhub.vr.rwth-aachen.de/VR-Group/pvt}}
      \end{cvitems}
    }
  \cventry
    {Internet of Things (IoT) Programmer}
    {Fraunhofer Institute for Applied Information Technology (FIT)}
    {Sankt Augustin, Germany}
    {February 2014 - June 2015}
    {
      \begin{cvitems}
        \item {Developed an automotive construction pipeline demo under the \textit{ebbits (enabling Business-based Internet of Things and Services)} EU research project.}
        \item {Developed a bluetooth module for triage bracelets under the \textit{BRIDGE (Bridging resource and agencies in large-scale emergency management)} EU research project.}
        \item {Extended an ad-hoc distress beacon prototype for mobile phones, increasing signal detection range in situations with multiple victims.}
      \end{cvitems}
    }
  \cventry
    {Game Programmer}
    {Startup Kitchen}
    {Istanbul, Turkey}
    {February 2013 - August 2013}
    {
      \begin{cvitems}
        \item {Contributed to the development of \textit{Kixel}, a real-time multiplayer football game for Facebook.}
        \item {Developed a match-three game prototype for Facebook.}
      \end{cvitems}
    }
  \cventry
    {Intern Graphics Programmer}
    {Chyron}
    {New York, United States}
    {May 2012 - August 2012}
    {
      \begin{cvitems}
        \item {Implemented a Collada digital asset exchange file importer for loading scene data into \textit{Chyron Lyric PRO}.}
        \item {Contributed to the implementation of an Alembic interchange file importer for loading visual effects into \textit{Chyron Lyric PRO}.}
      \end{cvitems}
    }
  \cventry
    {Intern Web Programmer}
    {Grupanya}
    {Istanbul, Turkey}
    {June 2011 - August 2011}
    {
      \begin{cvitems}
        \item {Implemented a typographical error checker using Damerau-Levenshtein edit distance.}
        \item {Developed a tool for relating user demographics to the offers they are interested in.}
      \end{cvitems}
    }
\end{cventries}
